A formal approach but practical approach in train regulation

### 2025-06-26 paper/main.tex
Extend future works

@@

\todo{Temporiser}
\todo{Réordonnancer}

>>>>

Currently, our model does not include timing aspects. While we can characterise correctness properties, we lack the ability to specify \emph{quality of service} constraints. We intend to add time to our model, in order to be able to specify how fast trains ought to reach their destinations.

Another aspect we did not explore is reordering trains. So far, train schedules are decided statically, which may lead to unwanted situations: e.g. a delayed train supposed to use a block first prevents other trains to use that block during the delay. Dynamic reordering of trains, while difficult to implement, could improve this situation. To a lesser extend, we could extend our model with alternatives: having a static schedule that allow multiple possible ordering, and deciding which is taken at runtime.

@@
